Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-04-19 R/CONUS_AOD.Rmd
assign non-land stations to closest state

```{r get_noaa_regions, include=FALSE}
# assign AERONET stations to states
tar_load(aer_stations)
aer_stations_sf <- st_as_sf(aer_stations, coords = c("lon", "lat"), crs = "epsg:4326")
sf::sf_use_s2(FALSE) # we were getting errors about the USA geometry otherwise
aer_stations_sf <- st_join(aer_stations_sf, usa)
dt <- merge(dt, aer_stations_sf, by = "Site_Name")
# some Site_Names don't fall within land polygons for whatever reason
dt[is.na(ID), table(Site_Name)]
# where are the sites that didn't fall within a state?
site_nostate <- st_as_sf(dt[is.na(ID), ][unique(Site_Name), .(Site_Name, `Site_Elevation(m)`, geometry), mult = "first"], crs = "epsg:4326")
# ggplot() +
#   geom_sf(data = usa, fill = NA) +
#   geom_sf(data = site_nostate, color = "red")
# what proportion of data are not in a state?
dt[, proportions(table(is.na(ID)))]
# assign these to the closest state
matched <- st_join(site_nostate,
                   usa,
                   join=nngeo::st_nn, k=1)
# plot these matchups
# ggplot() +
#   geom_sf(data = usa, fill = NA) +
#   geom_sf_text(data = matched, aes(label = toupper(substr(ID, 1, 1))), color = "red") + theme_minimal()

@@

# trying to get from state names to state abbreviations
dt[ , state.abb := state.abb[match(stringr::str_to_title(ID), state.name)]]
dt[is.na(state.abb), .(ID, Site_Name, geometry)][, table(Site_Name)]
dt[, state.noaa.region := factor(
   sapply(state.abb, USE.NAMES = F,
       function(sa) if (sa %in% c("AK", "HI")) NA else
           names(noaa.regions)[which(sapply(noaa.regions, function(r)
               sa %in% r))]),
   levels = names(noaa.regions))]
# unmatched locations
dt[is.na(state.noaa.region), .(ID, state.abb, Site_Name, geometry)][unique(Site_Name), , mult = "first"]
```

>>>>

```{r get_noaa_regions, include=FALSE}
# assign AERONET stations to states
tar_load(aer_stations)
aer_stations_sf <- st_as_sf(aer_stations, coords = c("lon", "lat"), crs = "epsg:4326")
sf::sf_use_s2(FALSE) # we were getting errors about the USA geometry otherwise
aer_stations_sf <- st_join(aer_stations_sf, usa)
dt <- merge(dt, aer_stations_sf, by = "Site_Name")
# some Site_Names don't fall within land polygons for whatever reason
dt[is.na(ID), table(Site_Name)]
# where are the sites that didn't fall within a state?
site_nostate <- st_as_sf(dt[is.na(ID), ][unique(Site_Name), .(Site_Name, `Site_Elevation(m)`, geometry), mult = "first"], crs = "epsg:4326")
# ggplot() +
#   geom_sf(data = usa, fill = NA) +
#   geom_sf(data = site_nostate, color = "red")
# what proportion of data are not in a state?
dt[, proportions(table(is.na(ID)))]
# assign these to the closest state
matched <- st_join(site_nostate,
                   usa,
                   join=nngeo::st_nn, k=1)
# plot these matchups
# ggplot() +
#   geom_sf(data = usa, fill = NA) +
#   geom_sf_text(data = matched, aes(label = toupper(substr(ID, 1, 1))), color = "red") + theme_minimal()
dt[as.data.table(matched, key = "Site_Name"), ID := i.ID]

@@

# trying to get from state names to state abbreviations
# ugly capitalization
dt[ , state.abb := state.abb.plusdc[match(stringr::str_to_title(ID), c(state.name, "District Of Columbia"))]]
dt[, state.noaa.region := factor(
   sapply(state.abb, USE.NAMES = F,
       function(sa) if (sa %in% c("AK", "HI")) NA else
           names(noaa.regions)[which(sapply(noaa.regions, function(r)
               sa %in% r))]),
   levels = names(noaa.regions))]
```
